Intentional release of native species undermines ecological stability

### 2022-10-21 rmd/supporting_info.Rmd
Update supporting_info.Rmd

---
output:
  bookdown::pdf_document2:
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 11pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath,fancyhdr, caption}
  - \captionsetup{width=1.3\linewidth, labelfont={bf}}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
nocite: |
  @duranteNoteMultiplicativeGamma2017, @myersMaximumReproductiveRate1999, @gotoEcologicalMorphologicalDivergence1975,@gotoLifeHistoryDistibution1981, @ministryofenvironmentofjapanThreatenedWildlifeJapan2014, @natsumedaEvaluationEcologicalFeatures2010, @fishbaseFishBaseHttpsWww
---

@@

**Fish release.** The release of masu salmon began in the 1950s. Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage). Although the fish release occurs at multiple locations within a watershed, the release information is available only at the watershed level. For each release stage, we assembled annual records of intentional release (the number of fish released; 1999-2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute. During the study period, the majority of release took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)

@@

```{=tex}
\begin{align}
\begin{split}
R'_s &= \eta_{w,s'} R_w\\
\sum_{s'}^{S_w + 1} \eta_{w,s'} &= 1
(\#eq:effr)
\end{split}
\end{align}
```
In Equation \@ref(eq:effr), $\eta_{w,s'}$ represents the effective proportion of total release affecting the community at site $s'$ within watershed $w$. The summation of $\eta_{w,s'}$ over $S_w+1$ is assumed to be unity because a non-negligible portion of release may escape into unsurveyed areas. Since the values of $\eta_{w,s'}$ are not available in our dataset, we estimated them through a stochastic search while fitting the regression model to the data within a Bayesian framework (see **model fitting**). Other site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use. Urban and agricultural land use was omitted because of either a limited value range (**Figure S**\@ref(fig:fig-env)) or a strong correlation with forest land use (**Figure S**\@ref(fig:fig-cor)). The watershed-specific intercept was related to a watershed-level predictor as:

@@

```{=tex}
\begin{align}
\begin{split}
N_{i,t} \sim \text{Poisson}(\lambda_{i,t} A_{t})\\
\lambda_{s,t} = n_{i,t}\exp(\varepsilon_{i,t}^{\text{obs}})
\end{split}
\end{align}
```
where $\varepsilon_{i,t}^{\text{obs}} \sim \text{Normal}(0, \sigma_{\text{obs},i})$. In the state model, we described a multi-species Ricker model for fish density $n_{i,t}$:

@@

The analysis of a two-species community revealed the distinct parameter space predicting a stabilizing, neutral, or destabilizing effect of intentional release. The left column in **Figure S**\@ref(fig:fig-2sp-w)**A** shows the predictions in scenarios with no environmental stochasticity ($\sigma_{\varepsilon} =$ `r min(list_param[[1]]$sd_env)`) and weak competition ($\bar{\alpha}=$ `r min(list_param[[1]]$alpha)`). For lower values of intrinsic growth rate $r_i$ ($<1.5$), intentional release had neutral (with higher $K$) to destabilizing effects (with lower $K$) on community dynamics. In the meantime, stabilization with intentional release occurred for higher values of $r_i$ ($\ge 1.5$) by dampening limit cycles or chaos (**Figure S**\@ref(fig:fig-2sp-s)), which is reflected in decreased SD $\sigma$ (**Figure S**\@ref(fig:fig-2sp-w)). However, the long-term mean of community density $\mu$ consistently decreased with intentional release in almost all cases except for only a few combinations of $r_i$ and $K$ (**Figure S**\@ref(fig:fig-2sp-w)).

>>>>

---
output:
  bookdown::pdf_document2:
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 10.5pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath,fancyhdr, caption}
  - \captionsetup{width=1.3\linewidth, labelfont={bf}}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
nocite: |
  @duranteNoteMultiplicativeGamma2017, @myersMaximumReproductiveRate1999, @gotoEcologicalMorphologicalDivergence1975,@gotoLifeHistoryDistibution1981, @ministryofenvironmentofjapanThreatenedWildlifeJapan2014, @natsumedaEvaluationEcologicalFeatures2010, @fishbaseFishBaseHttpsWww
---

@@

**Fish release.** The release of masu salmon began in the 1950s. Although the program aims to release a constant number of hatchery fish for each watershed, uncontrollable factors (e.g., disease, budget allocation) produce some variation in the number of releases among years. Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage). Most fish are released near the fish survey sites. However, the number of fish released at each site was reported as an aggregate for each watershed, and the site-specific information of release is unavailable. For each release stage, we assembled annual records of intentional release (the number of fish released; 1999 -- 2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute. During the study period, the majority of release took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)

@@

```{=tex}
\begin{align}
\begin{split}
R'_s = \eta_{w,s'} R_w~\text{where}~
\sum_{s'}^{S_w + 1} \eta_{w,s'} = 1
(\#eq:effr)
\end{split}
\end{align}
```
In Equation \@ref(eq:effr), $\eta_{w,s'}$ represents the effective proportion of total release affecting the community at site $s'$ within watershed $w$. The summation of $\eta_{w,s'}$ over $S_w+1$ is assumed to be unity because a non-negligible portion of release may escape into unsurveyed areas. Since the values of $\eta_{w,s'}$ are not available in our dataset, we estimated them through a stochastic search while fitting the regression model to the data within a Bayesian framework (see **model fitting**). Other site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use. Urban and agricultural land use was omitted because of either a limited value range (**Figure S**\@ref(fig:fig-env)) or a strong correlation with forest land use (**Figure S**\@ref(fig:fig-cor)). The watershed-specific intercept was related to a watershed-level predictor as:

@@

```{=tex}
\begin{align}
\begin{split}
N_{i,t} &\sim \text{Poisson}(\lambda_{i,t} A_{t})\\
\lambda_{s,t} &= n_{i,t}\exp(\varepsilon_{i,t}^{\text{obs}})
\end{split}
\end{align}
```
where $\varepsilon_{i,t}^{\text{obs}} \sim \text{Normal}(0, \sigma_{\text{obs},i})$. In the state model, we described a multi-species Ricker model for fish density $n_{i,t}$:

@@

The analysis of a two-species community revealed the distinct parameter spaces predicting a stabilizing, neutral, or destabilizing effect of intentional release. The left column in **Figure S**\@ref(fig:fig-2sp-w)**A** shows the predictions in scenarios with no environmental stochasticity ($\sigma_{\varepsilon} =$ `r min(list_param[[1]]$sd_env)`) and weak competition ($\bar{\alpha}=$ `r min(list_param[[1]]$alpha)`). For lower values of intrinsic growth rate $r_i$ ($<1.5$), intentional release had neutral (with higher $K$) to destabilizing effects (with lower $K$) on community dynamics. In the meantime, stabilization with intentional release occurred for higher values of $r_i$ ($\ge 1.5$) by dampening limit cycles or chaos (**Figure S**\@ref(fig:fig-2sp-w)), which is reflected in decreased SD $\sigma$ (**Figure S**\@ref(fig:fig-2sp-w)). However, the long-term mean of community density $\mu$ consistently decreased with intentional release in almost all cases except for only a few combinations of $r_i$ and $K$ (**Figure S**\@ref(fig:fig-2sp-w)).
